Sketch of DP - Bayesian Inference

### 2018-07-08 main-sketch.tex
fix plots 1

\begin{document}
\title{Template for ACM CCS 2017} % TODO: replace with your title

@@

\keywords{template; formatting; pickling} % TODO: replace with your keywords

@@

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{Accuracy_VS_Prior_mean.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
\label{fig_vs_prior_variance}
\end{figure}

>>>>

\begin{document}
\title{Sketch of DP - Bayesian Inference} % TODO: replace with your title

@@

\keywords{differential privacy, Bayesian inference, Hellinger distance} % TODO: replace with your keywords

@@

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{Accuracy_VS_Prior_mean.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.00000001$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
\label{fig_vs_prior_variance}
\end{figure}
